SPARQL on the Open, Decentralised Web

### 2016-11-16 dissertation/conclusions.tex
flow into prefetcher, fixes #25

>>>>

Finally, the work extended to a SPARQL query engine that could run on
a proxy. It could cache intermediate results of triple pattern
matches, either in real time or by prefetching results that might be
valuable. In query planning and evaluation, it could use the cache, a
remote SPARQL endpoint and a Triple Pattern Fragments
server. Unfortunately, this work had to be ended before it could reach
a conclusion, but a detailed account of the work is included in
Chapther~\ref{sec:tpfcacheplanning}.
